### 2021-04-12 Chapter-5/Chapter-5.tex
Updates from Overleaf

\begin{figure}[ht]
  \centering
  \includegraphics[width=\columnwidth]{./figures/chapter5/channel.pdf}
  \caption{The relationship between the side-channel attack and the channel capacity. For a deterministic program, the side-channel attack can be seen as the communication between the observation ($o \in O$) and the secret ($k \in K$) via a discrete memoryless channel.}
  \label{fig:side_channel}
\end{figure}

@@

According to Chi Square Distribution Table, we have the probability $p\approx0.95$ to accept the null hypothesis for the two leakages in Figure~\ref{chapter5:fig:multiple} (a). We have the probability $p\approx0.00$ to accept the null hypothesis for the two leakages in Figure~\ref{chapter5:fig:multiple} (b).
\section{Design}
In this section, we explain the implementation of \ctool{}.
we first present the overview of \ctool{}. After that, we discuss some design details to implement \ctool{}.

>>>>

\begin{figure}[ht]
  \centering
  \includegraphics[width=.8\columnwidth]{./figures/chapter5/channel.pdf}
  \caption{The relationship between the side-channel attack and the channel capacity. For a deterministic program, the side-channel attack can be seen as the communication between the observation ($o \in O$) and the secret ($k \in K$) via a discrete memoryless channel.}
  \label{fig:side_channel}
\end{figure}

@@

According to Chi Square Distribution Table, we have the probability $p\approx0.95$ to accept the null hypothesis for the two leakages in Figure~\ref{chapter5:fig:multiple} (a). We have the probability $p\approx0.00$ to accept the null hypothesis for the two leakages in Figure~\ref{chapter5:fig:multiple} (b). Therefore, we infer that the two leakages in Figure~\ref{chapter5:fig:multiple} (a) are independent. And the two leakages Figure~\ref{chapter5:fig:multiple} (b) are dependent. For each leakage points, we use the above method to test if any two leakage sites are independent. We combine them into a leakage are calculate the total amount of the leakage.
\section{Design}
In this section, we explain the implementation of \ctool{}.
we first present the overview of \ctool{}. After that, we discuss some design details to implement \ctool{}.
